Flexible, high throughput data extraction from primary literature: The metaDigitise R package

### 2017-10-31 docs/manuscript.tex
manuscript figures update with iris data

\begin{figure}[ht] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_plot_type.pdf} 
 \caption{Plot types that metaDigitise is designed to extract data from: A) mean and error plot, B) box plot, C) scatter plot and D) histogram. }
\label{fig:plot_type}
\end{figure}

@@

>>>>

\begin{figure}[ht] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_plot_type.pdf} 
 \caption{Four plot types that metaDigitise is designed to extract data from: A) mean and error plot, B) box plot, C) scatter plot and D) histogram. Data is taken from the iris dataset in R. A and B are plotted with the whole dataset, C and D are just the data for the species setosa.}
\label{fig:plot_type}
\end{figure}

@@

\begin{figure}[!h] 
%\onehalfspacing
 \includegraphics[width=0.9\textwidth]{fig_all_extract.pdf} 
 \caption{ }
\label{fig:all_extract}
\end{figure}
